### 2023-10-25 chapters/discussion.tex
Add todo

@@

\section{Representation learning with variational autoencoders}
%
In this thesis we studied two different approaches to speech representation learning: VAEs in \cref{chp:paper-hierarchical,chp:paper-mo?delagnostic,chp:paper-benchmarking} and self"=supervised methods in \cref{chp:paper-review}. 
As we saw, the probabilistic formulation of VAEs provides benefits for their application to uncertainty quantification, although competitive methods that use self"=supervised foundation models have also been proposed \textcite{xiao_we_2021,hendrycks_using_2019,bergman_classificationbased_2020}. Self"=supervised methods are generally superior when it comes to performance on downstream tasks. While this of course depends on the task and the amount and type of unlabeled and labeled data, self"=supervised methods for speech are commonly evaluated on downstream tasks that are harder and more complex than those used for VAEs. For instance, between \cref{tab: phoneme recognition (PER),tab:unsupervisedASR} self"=supervised methods can be seen to outperform VAEs for phoneme recognition while self"=supervised methods are also reported for word-level speech recognition. 
In the following, we will discuss potential directions of future research that might help shed light on why representations from VAEs underperform on downstream tasks and how they might be improved.

@@

\subsection{Masking} 
As discussed in \cref{chp:paper-review}, masking is one of the driving techniques behind the success of self"=supervised methods for speech \parencite{devlin_bert_2018,baevski_wav2vec_2020}. By removing tokens from the input or an early feature extraction layer and tasking a model with inferring their representations, models are forced to learn how neighboring tokens relate to those masked. Depending on the size of the mask, these dependencies can be more or less semantic in nature. For instance, the wav2vec 2.0 model is well-known to learn representations that have high similarity with word identity and meaning \parencite{pasad_layerwise_2021}.

@@

% \section{\Cref{chp:paper-review} revisited: \dots} \label{sec:discussion-paper-review}

>>>>

\todo[inline]{Unsupervised representation learning for medical applications. We tried BERT for stroke but no success. Medical coding state-of-the-art uses pretrained BERT, but only marginally improves upon simpler baselines.}

@@

\section{Representation learning with variational autoencoders}
%
In this thesis we studied two different approaches to speech representation learning: VAEs in \cref{chp:paper-hierarchical,chp:paper-modelagnostic,chp:paper-benchmarking} and self"=supervised methods in \cref{chp:paper-brief}. 
As we saw, the probabilistic formulation of VAEs provides benefits for their application to uncertainty quantification, although competitive methods that use self"=supervised foundation models have also been proposed \textcite{xiao_we_2021,hendrycks_using_2019,bergman_classificationbased_2020}. Self"=supervised methods are generally superior when it comes to performance on downstream tasks. While this of course depends on the task and the amount and type of unlabeled and labeled data, self"=supervised methods for speech are commonly evaluated on downstream tasks that are harder and more complex than those used for VAEs. For instance, between \cref{tab: phoneme recognition (PER),tab:unsupervisedASR} self"=supervised methods can be seen to outperform VAEs for phoneme recognition while self"=supervised methods are also reported for word-level speech recognition. 
In the following, we will discuss potential directions of future research that might help shed light on why representations from VAEs underperform on downstream tasks and how they might be improved.

@@

\subsection{Masking} 
As discussed in \cref{chp:paper-brief}, masking is one of the driving techniques behind the success of self"=supervised methods for speech \parencite{devlin_bert_2018,baevski_wav2vec_2020}. By removing tokens from the input or an early feature extraction layer and tasking a model with inferring their representations, models are forced to learn how neighboring tokens relate to those masked. Depending on the size of the mask, these dependencies can be more or less semantic in nature. For instance, the wav2vec 2.0 model is well-known to learn representations that have high similarity with word identity and meaning \parencite{pasad_layerwise_2021}.

@@
